---
title: "CLV_online Gaming Community"
output: html_document
---



```{r}
library(readxl)
library(Hmisc)
library(MASS)
library(caret)
library(regclass)
library(ISLR)
library(boot)
library(vcd)
library(pROC)
library (ROCR)
library(dplyr)
library(tidyverse)
```

## Difference in differences (DiD) Regression Model to  determine whether Campaigns have significant impact on Revenue.
```{r}
setwd("C:/Users/dell/Downloads/.")

KyngaCell_df<-read_excel("C:/Rishabh/KyngaCell.xlsx",sheet = 4)


data_filtered <- KyngaCell_df[,c(1,2,3,4,6)]
data_stacked <- pivot_longer(data_filtered, cols = c(3,4), names_to = "Period", values_to = "Revenue")
Revenue<-data_stacked$Revenue
Join<-data_stacked$`Joined?`
Before<-ifelse(data_stacked$Period == "Month Before", 1, 0)
After<-ifelse(data_stacked$Period == "Month After", 1, 0)
Campaign <- data_stacked$`Campaign/Organic`


model<-lm(Revenue ~ Join + After + Campaign+ Join:After )
summary(model)


```

### Interpretation for effect of Campaign on Revenue.
#### #Since p -value is insignificant for the  expalanatory variable Campaign , we do not have sufficient evidence to conclude whether there is significant impact on revenue or customers joining the online community due to Campaign.



<br>


## Logistics Regression Model
#### #Determining Probability of Churn of Consumer

```{r}

Churn <- KyngaCell_df$`Churned at 3 months`
ID <- KyngaCell_df$`Customer ID`
Age <- KyngaCell_df$`Customer Age with Firm at time of launching the online community`
Spend <- KyngaCell_df$`Average Spend Last 3 months of Life with the firm`
Join <- KyngaCell_df$`Joined?`
Campaign <- KyngaCell_df$`Campaign/Organic`
mylogit<-glm(Churn~Join+Age+Spend+Campaign, data=KyngaCell_df, family=binomial(link="logit"))
summary(mylogit) 
confint(mylogit) 
AIC(mylogit)


preddata<-with(KyngaCell_df,data.frame(ID,Join,Age,Spend,Campaign))
probchurn<-predict(mylogit,newdata=preddata,type="response")
predchurn<-ifelse(probchurn > 0.5, 1,0)
missclass<-predchurn!=Churn
misclasserror<-mean(predchurn!=Churn)		
print(paste('Accuracy',1-misclasserror))

confMat2<-confusionMatrix(data = as.factor(predchurn),reference = as.factor(Churn),positive = "1")
confMat2

finaldata<-cbind(KyngaCell_df,probchurn,predchurn,missclass)
View(finaldata)

```

## Computing the Retention rate and CLV with Campaign
```{r}

campaign <- subset(finaldata, finaldata$`Campaign/Organic` == 1)
organic <- subset(finaldata, finaldata$`Campaign/Organic` == 0)
churn_campaign <- mean(campaign$probchurn)
retention_campaign <- 1 - churn_campaign
retention_campaign
churn_organic <- mean (organic$probchurn)
ret_organic <- 1 - churn_organic
ret_organic



#####Computing CLV new for Campaign and organic

AC <- 0
i <- 0.1

m1_campaign <- 0.5 * campaign$`Average Spend Last 3 months of Life with the firm`
m1_organic <- 0.5 * organic$`Average Spend Last 3 months of Life with the firm`



L_campaign <- 1/(1-retention_campaign)
L_organic <- 1/(1-ret_organic)


Basic_CLV_campaign <- m1_campaign * L_campaign - AC
mean(Basic_CLV_campaign)

Basic_CLV_organic <- m1_organic * L_organic - AC
mean(Basic_CLV_organic)



#CLV Lifetime

CLV_campaign <- m1_campaign * ((1 + i) / (1 + i - retention_campaign))

CLV_organic <- m1_organic * ((1 + i) / (1 + i - ret_organic))

mean(CLV_campaign)
mean(CLV_organic)


# Checking if there is significant difference in CLV values after Campaign

t.test(CLV_campaign, CLV_organic, alternative = "two.sided")




```
##### #Since p-value is insignificant for  we can conclude that there is no much difference in CLV values of the customers who joined through Campaign or Organic.


